Off the beaten path: \\ Gaia reveals GD-1 stars outside of the main stream

### 2018-06-21 paper/gd1.tex

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{density-model.pdf}
\end{center}
\caption{
{\bf \emph{Top row}: Density of stars in $\phi_2$ (grey) and inferred density (black curve) for regions around the spur, blob, and a control field.
The model for the density includes components for the stream, background, and a feature overdensity (the spur or the blob), but with amplitudes that are allowed to go to zero (see \sectionname~\ref{sec:res_gap} for more details.)
\emph{Bottom row}: Inferred posterior probability distributions over the amplitude ($\alpha$) of each component in each field: $\alpha_{\textrm{s}}$ for the stream, $\alpha_{\textrm{bg}}$ for the background, and $\alpha_{\textrm{f}}$ for the feature.
In both feature fields, the model prefers an additional component to describe the feature, whereas in the control field the density is consistent with stream + background.}
}
\label{fig:density-model}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{density-model.pdf}
\end{center}
\caption{
\changes{\emph{Top row}: Density of stars in $\phi_2$ (grey) and inferred density (black curve) for regions around the spur, blob, and a control field.
The model for the density includes components for the stream, background, and a feature overdensity (the spur or the blob), but with amplitudes that are allowed to go to zero (see \sectionname~\ref{sec:res_gap} for more details.)
\emph{Bottom row}: Inferred posterior probability distributions over the amplitude ($\alpha$) of each component in each field: $\alpha_{\textrm{s}}$ for the stream, $\alpha_{\textrm{bg}}$ for the background, and $\alpha_{\textrm{f}}$ for the feature.
In both feature fields, the model prefers an additional component to describe the feature, whereas in the control field the density is consistent with stream + background.}
}
\label{fig:density-model}
\end{figure}
